### 2018-03-01 tex/paper.tex
Answer some questions and add citation

\sjtnote{Still true? CHECK} Finally, a running contract will initiate a number of payment actions on the blockchain at each step, represented by a list of actions.

@@

We have examined a single kind of commitment, namely a commitment of a certain amount of currency. In different applications, such as on-chain game playing of games like poker, a commitment to a value will be required. A value commitment would include a choice of a play in a game, which would be chosen and concealed from the other players until a later point in play, when it can be revealed. \sjtnote{Add citation to the poker paper?}

>>>>

Finally, payments can be granted by using committed money, but they must be manually redeemed by the recipient, in the 
same way that cash commitments are redeemed when they expire. The effects of the contract in the blockchain are 
represented by a list of actions that is derived from the execution of each step of the semantics.

@@

We have examined a single kind of commitment, namely a commitment of a certain amount of currency. In different 
applications, such as on-chain game playing of games like poker, a commitment to a value will be required. A value 
commitment would include a choice of a play in a game, which would be chosen and concealed from the other players until 
a later point in play, when it can be revealed. The paper \cite{kumaresan2015use} makes use of this and other 
cryptographic primitives to enforce the rules of poker while maintaining the cards of each player secret.
